Plug-and-play dual-tree algorithm runtime analysis

### 2015-08-14 bounds-files/sec02-nearest-neighbor-search.tex
Refactor for consistent use of O(N).

\begin{thm}
Using cover trees, the standard cover tree pruning dual-tree traversal, and the
nearest neighbor search \texttt{BaseCase()} and \texttt{Score()} as given in
Algorithms \ref{alg:nn_base_case} and \ref{alg:nn_score}, respectively, and also
given a reference set $S_r$ with expansion constant $c_r$, and a query set $S_q$,
the running time of the algorithm is bounded by $O(c_r^4 c_{qr}^5 (N +
I_t(\mathscr{T}_q) + \theta))$ with $I_t(\mathscr{T}_q$ and $\theta$ defined as
in Definition \ref{def:imbalance} and Lemma \ref{lem:extcase3}, respectively.
\label{thm:nns}
\end{thm}

>>>>

\begin{thm}
Using cover trees, the standard cover tree pruning dual-tree traversal, and the
nearest neighbor search \texttt{BaseCase()} and \texttt{Score()} as given in
Algorithms \ref{alg:nn_base_case} and \ref{alg:nn_score}, respectively, and also
given a reference set $S_r$ of size $O(N)$ with expansion constant $c_r$, and a
query set $S_q$ of size $O(N)$, the running time of the algorithm is bounded by
$O(c_r^4 c_{qr}^5 (N + I_t(\mathscr{T}_q) + \theta))$ with $I_t(\mathscr{T}_q)$
and $\theta$ defined as in Definition \ref{def:imbalance} and Lemma
\ref{lem:extcase3}, respectively.
\label{thm:nns}
\end{thm}
